---
title: "Introduction to myLog"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to myLog}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# myLog: Logistic Regression Package

This vignette demonstrates the core features of the `myLog` package, including training logistic regression models, making predictions, and preprocessing data.

## Installation

Install the package using:

```r
# Install devtools if not already installed
install.packages("devtools")

# Install from GitHub
devtools::install_github("tunbo777/myLog")
```

## Example: Dara preprocessing
```{r, echo = TRUE, results = "markup",eval = TRUE}
library(myLog)

set.seed(123)
X <- matrix(rnorm(100), ncol = 5)
y <- sample(0:1, 20, replace = TRUE)
processed <- prepare_data(X, y)

# View processed data
head(processed$X)
```

## Example: Training a logistics regression model
```{r, echo = TRUE, results = "markup",eval = TRUE}

# Train the model
model <- train_logistic(X, y)

# View model coefficients
print(model$coefficients)
```

## Example: Making predictions
```{r, echo = TRUE, results = "markup",eval = TRUE}
# Predict probabilities
predictions <- predict_logistic(model, X)

# View predictions
head(predictions)
```

## Comparison: Compared with orginical R function
```{r, echo = TRUE, results = "markup",eval = TRUE}
# Train logistic model using myLog
my_model <- train_logistic(X, y)

# Train logistic model using glm() in R
df <- data.frame(y = y, X)
glm_model <- glm(y ~ ., data = df, family = binomial)

# Compare the coefficients
all.equal(as.numeric(coef(glm_model)), as.numeric(my_model$coefficients))

# Compare the efficiency
library(bench)

bench_results <- bench::mark(
  MyLogistic = train_logistic(X, y),
  R_glm = glm(y ~ ., data = df, family = binomial),
  check = FALSE
)

print(bench_results)
```



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(myLog)
```
